### 2021-10-12 chapters/conclusion.tex
removed unwanted files from tracking

    The lifetimes of post-merger remnants are highly uncertain with gravitational-wave timescales ranging from $0.15-12\,\s$ for a range of ellipticities and equations of state (Eq.~\ref{eq:Intro:GWAngularMomentumLoss}).
    If the above waveform systematics are successfully addressed then detection and parameter estimation studies could be performed with much longer collapse times. 
    A successful injection study for collapse times up to $\sim 2\,\s$ may allow the measurement of collapse times for future GW170817-like events.
    This would have significantly aided model selection for the gamma-ray physics associated with GRB 170817A.\par

>>>>

    The lifetimes of post-merger remnants are highly uncertain with gravitational-wave timescales ranging from $0.15-12\,\s$ for a range of ellipticities and equations of state (Eq.(\ref{eq:Intro:GWAngularMomentumLoss})).
    If the above waveform systematics are successfully addressed then detection and parameter estimation studies could be performed with much longer collapse times. 
    A successful injection study for collapse times up to $\sim 2\,\s$ may allow the measurement of collapse times for future GW170817-like events.
    This would have significantly aided model selection for the gamma-ray physics associated with GRB 170817A.\par

### 2021-10-12 papers/paper2.tex
removed unwanted files from tracking

        We inject numerical-relativity waveforms at various post-merger signal-to-noise ratios into a three-detector network (LIGO Hanford, Livingston, and Virgo) at design sensitivity for each interferometer~\cite{PSD:aLIGO,PSD:aVirgo}. 
        We inject the post-merger signal at a fixed time and fixed sky position, assuming that we know the coalescence time from the inspiral stage. 
        In Section~\ref{sec:sensitivity2} we test this assumption by determining the uncertainty in the coalescence time for various signal-to-noise ratios.
        We use the {\textsc{Bilby}} package  \cite{Ashton2019} with the {\textsc{Dynesty}} sampler~\cite{Speagle2019} to sample posteriors, $p(\boldsymbol{\theta}|d)$, of the model parameters  using the likelihood, $\mathcal{L}(d | \boldsymbol{\theta})$, as follows:
        \begin{align}
        	p(\boldsymbol{\theta}|d) & =\dfrac{\mathcal{L}(d | \boldsymbol{\theta})\pi(\boldsymbol{\theta})}{\mathcal{Z}},\label{eq:posterior2}\\
        	\mathcal{Z} & =\int_{\boldsymbol{\theta}} d\boldsymbol{\theta} \mathcal{L}(d | \boldsymbol{\theta})\pi(\boldsymbol{\theta}),\label{eq:evidence2}\\
        	\mathcal{L}(d | \boldsymbol{\theta}) & \propto \exp\Big[-\Big<d(t)-h(\boldsymbol{\theta},t),d(t)-h(\boldsymbol{\theta},t)\Big>\Big]\label{eq:likelihood2}. 
        \end{align}        
        Here, $d(t)=s(t)+n(t)$ is the numerical-relativity waveform, $s(t)$, injected into noise, $n(t)$. 
        We simulate ten different Gaussian noise realisations with {\textsc{Bilby}}, to examine the response of the model to variations in detector noise. 
        We limit this to ten noise realisations to keep the computation time manageable.
        The priors on the model parameters are $\pi(\boldsymbol{\theta})$. 
        The noise-weighted inner product in Eq.~\ref{eq:likelihood2} is defined by:
        \begin{align}
        	\left<h_1,h_2\right>\equiv4\, \mathrm{Re} \int df\frac{\tilde{h}_1(f)\tilde{h}^{*}_2(f)}{S_h(f)},\label{eq:inner_product2}
        \end{align}
    where $S_h$ is the detector's noise power spectral density.
    We use a sampling frequency of 16384\,Hz to eliminate aliasing of the upper sidebands. 
    We use constrained priors to sort the maximum amplitude for $\tilde{h}_{j,+}(\boldsymbol{\theta},f)$, such that  $|\tilde{h}_{j,+}(\boldsymbol{\theta},f)|_{max} > |\tilde{h}_{j+1,+}(\boldsymbol{\theta},f)|_{max}$.
    This ensures that the mode zero ($j=0$) exponentially damped sinusoid corresponds to the dominant post-merger frequency. 
    Full details on the priors are given in Appendix~\ref{appendix:b2}. 
    The optimal post-merger signal-to-noise ratio, $\rho_{\mathrm{opt}}$, is calculated from the quadrature sum of the optimal post-merger signal-to-noise ratio for each of the three detectors, $\rho_{\mathrm{opt},i}$ as follows:
\begin{equation}
    \rho_{\mathrm{opt}}^2 = \sum_{i \in  \mathrm{HLV}} \rho_{\mathrm{opt},i}^2\quad,\label{eq:OptimalSNR2}
\end{equation}
    for $t \geq 0$.
    The matched filter signal-to-noise ratio for a single detector is given by:
\begin{equation}
    \rho_{mf} = \frac{\left<d, h(\boldsymbol{\theta})\right>}{\left< h(\boldsymbol{\theta}),h(\boldsymbol{\theta})\right>^\frac{1}{2}}\quad.\label{eq:MatchedFilterSNR2}
\end{equation} \par

@@

     To measure the extent of the waveform mismatch, we calculate the noise-weighted fitting factor between the injected numerical-relativity waveform, $d(t)$, and the posterior waveform, $h(\boldsymbol{\theta},t)$, ~\cite{Apostolatos95}:
    \begin{equation}
    	\mathcal{F}(d(t),h(\boldsymbol{\theta},t))\equiv\frac{\left<d(t)|h(\boldsymbol{\theta},t)\right>}{\sqrt{\left<d(t)|d(t)\right>\left<h(\boldsymbol{\theta},t)|h(\boldsymbol{\theta},t)\right>}}.\label{eq:FF2}
    \end{equation}
    The fitting factor, calculated with noise from one detector at Advanced LIGO design sensitivity~\cite{PSD:aLIGO}, quantifies the loss in signal-to-noise due to signal mismatch in relation to an optimal signal-to-noise ratio, Eq.~\ref{eq:OptimalSNR2}. \par

@@

     The matched filter signal-to-noise ratio is calculated using Eq.~\ref{eq:MatchedFilterSNR2} with a single detector at Advanced LIGO sensitivity.

@@

    In addition to the aforementioned analytical models~\cite{Bauswein2016,Bose2018}, other work have generated analytical post-merger gravitational-wave  models. 
    In Ref.~\cite{Hotokezaka2013}, a model  was generated for the time-based amplitude and phase of the complex gravitational-wave strain using a smooth piece-wise function for the amplitude. 
    The time-based phase was fit by the combination of a polynomial and exponentially-damped sinusoid using an iterative CMA-ES (covariance matrix adaption evolution search) fitting algorithm.
    The maximum fitting factors were  calculated in the time domain without noise weighting and are not directly comparable to the noise-weighted fitting factors calculated with Eq.~\ref{eq:inner_product2}.
    The maximum fitting factors were  $\sim\!0.92\,$\nobreakdash-$\,0.98$ for 95\% of the 54 waveforms.\par

@@

    The priors are listed in Eqs.~\ref{eq:firstprior2}\Hyphdash*\ref{eq:w012} with $\mathcal{U}(a,b)$ representing a uniform prior distribution from $a$ to $b$. 

@@

    These restrictions are enforced in addition to the standard priors. The prior in Eq.~\ref{eq:modesorting2} ensures that the maximum spectral amplitude of each mode is decreasing. 

>>>>

        We inject numerical-relativity waveforms at various post-merger signal-to-noise ratios into a three-detector network (LIGO Hanford, Livingston, and Virgo) at design sensitivity for each interferometer~\cite{PSD:aLIGO,PSD:aVirgo}. 
        We inject the post-merger signal at a fixed time and fixed sky position, assuming that we know the coalescence time from the inspiral stage. 
        In Section~\ref{sec:sensitivity2} we test this assumption by determining the uncertainty in the coalescence time for various signal-to-noise ratios.
        We use the {\textsc{Bilby}} package  \cite{Ashton2019} with the {\textsc{Dynesty}} sampler~\cite{Speagle2019} to sample posteriors, $p(\boldsymbol{\theta}|d)$, of the model parameters  using the likelihood, $\mathcal{L}(d | \boldsymbol{\theta})$, as follows:
        \begin{align}
        	p(\boldsymbol{\theta}|d) & =\dfrac{\mathcal{L}(d | \boldsymbol{\theta})\pi(\boldsymbol{\theta})}{\mathcal{Z}},\label{eq:posterior2}\\
        	\mathcal{Z} & =\int_{\boldsymbol{\theta}} d\boldsymbol{\theta} \mathcal{L}(d | \boldsymbol{\theta})\pi(\boldsymbol{\theta}),\label{eq:evidence2}\\
        	\mathcal{L}(d | \boldsymbol{\theta}) & \propto \exp\Big[-\Big<d(t)-h(\boldsymbol{\theta},t),d(t)-h(\boldsymbol{\theta},t)\Big>\Big]\label{eq:likelihood2}. 
        \end{align}        
        Here, $d(t)=s(t)+n(t)$ is the numerical-relativity waveform, $s(t)$, injected into noise, $n(t)$. 
        We simulate ten different Gaussian noise realisations with {\textsc{Bilby}}, to examine the response of the model to variations in detector noise. 
        We limit this to ten noise realisations to keep the computation time manageable.
        The priors on the model parameters are $\pi(\boldsymbol{\theta})$. 
        The noise-weighted inner product in Eq.(\ref{eq:likelihood2}) is defined by:
        \begin{align}
        	\left<h_1,h_2\right>\equiv4\, \mathrm{Re} \int df\frac{\tilde{h}_1(f)\tilde{h}^{*}_2(f)}{S_h(f)},\label{eq:inner_product2}
        \end{align}
    where $S_h$ is the detector's noise power spectral density.
    We use a sampling frequency of 16384\,Hz to eliminate aliasing of the upper sidebands. 
    We use constrained priors to sort the maximum amplitude for $\tilde{h}_{j,+}(\boldsymbol{\theta},f)$, such that  $|\tilde{h}_{j,+}(\boldsymbol{\theta},f)|_{max} > |\tilde{h}_{j+1,+}(\boldsymbol{\theta},f)|_{max}$.
    This ensures that the mode zero ($j=0$) exponentially damped sinusoid corresponds to the dominant post-merger frequency. 
    Full details on the priors are given in Appendix~\ref{appendix:b2}. 
    The optimal post-merger signal-to-noise ratio, $\rho_{\mathrm{opt}}$, is calculated from the quadrature sum of the optimal post-merger signal-to-noise ratio for each of the three detectors, $\rho_{\mathrm{opt},i}$ as follows:
\begin{equation}
    \rho_{\mathrm{opt}}^2 = \sum_{i \in  \mathrm{HLV}} \rho_{\mathrm{opt},i}^2\quad,\label{eq:OptimalSNR2}
\end{equation}
    for $t \geq 0$.
    The matched filter signal-to-noise ratio for a single detector is given by:
\begin{equation}
    \rho_{mf} = \frac{\left<d, h(\boldsymbol{\theta})\right>}{\left< h(\boldsymbol{\theta}),h(\boldsymbol{\theta})\right>^\frac{1}{2}}\quad.\label{eq:MatchedFilterSNR2}
\end{equation} \par

@@

     To measure the extent of the waveform mismatch, we calculate the noise-weighted fitting factor between the injected numerical-relativity waveform, $d(t)$, and the posterior waveform, $h(\boldsymbol{\theta},t)$, ~\cite{Apostolatos95}:
    \begin{equation}
    	\mathcal{F}(d(t),h(\boldsymbol{\theta},t))\equiv\frac{\left<d(t)|h(\boldsymbol{\theta},t)\right>}{\sqrt{\left<d(t)|d(t)\right>\left<h(\boldsymbol{\theta},t)|h(\boldsymbol{\theta},t)\right>}}.\label{eq:FF2}
    \end{equation}
    The fitting factor, calculated with noise from one detector at Advanced LIGO design sensitivity~\cite{PSD:aLIGO}, quantifies the loss in signal-to-noise due to signal mismatch in relation to an optimal signal-to-noise ratio, Eq.(\ref{eq:OptimalSNR2}). \par

@@

     The matched filter signal-to-noise ratio is calculated using Eq.(\ref{eq:MatchedFilterSNR2}) with a single detector at Advanced LIGO sensitivity.

@@

    In addition to the aforementioned analytical models~\cite{Bauswein2016,Bose2018}, other work have generated analytical post-merger gravitational-wave  models. 
    In Ref.~\cite{Hotokezaka2013}, a model  was generated for the time-based amplitude and phase of the complex gravitational-wave strain using a smooth piece-wise function for the amplitude. 
    The time-based phase was fit by the combination of a polynomial and exponentially-damped sinusoid using an iterative CMA-ES (covariance matrix adaption evolution search) fitting algorithm.
    The maximum fitting factors were  calculated in the time domain without noise weighting and are not directly comparable to the noise-weighted fitting factors calculated with Eq.(\ref{eq:inner_product2}).
    The maximum fitting factors were  $\sim\!0.92\,$\nobreakdash-$\,0.98$ for 95\% of the 54 waveforms.\par

@@

    The priors are listed in Eqs.(\ref{eq:firstprior2}\Hyphdash*\ref{eq:w012}) with $\mathcal{U}(a,b)$ representing a uniform prior distribution from $a$ to $b$. 

@@

    These restrictions are enforced in addition to the standard priors. The prior in Eq.(\ref{eq:modesorting2}) ensures that the maximum spectral amplitude of each mode is decreasing. 

### 2021-10-12 papers/paper3.tex
removed unwanted files from tracking

        The gravitational waves from the post-merger remnant are modelled as a third-order, exponentially-damped sinusoid with a linear frequency-drift term. The plus polarisation of the gravitational-wave strain, $h_{+}(\boldsymbol{\theta},t)$, is given by: 
\begin{align}
        h_{+}(\boldsymbol{\theta},t) & = \sum_{j} h_{j,+}(\boldsymbol{\theta},t),\nonumber\\
        h_{j,+}(\boldsymbol{\theta},t) & = 
        H w_j \exp\left[-\frac{t}{T_j}\right] \cos \left(2\pi f_j t\left[1+\alpha_j t\right]+\psi_j \right),\nonumber\\
        \boldsymbol{\theta} & = \{H,w_j,T_j,f_j,\alpha_j,\psi_j :  j \in [0,2] \},\label{eq:hplus3}
\end{align}
    where $\boldsymbol{\theta}$ are the model parameters and $\sum_{j} w_j=1$. 
    Here, $H$ is an overall amplitude scaling factor, $w_j$ is the relative amplitude of the $j$th mode, $T_j$ is the corresponding exponential damping time constant, and $f_j$ is the corresponding frequency.
    The linear frequency-drift term is $\alpha_j$ and the initial phase  is $\psi_j$.
    The time, $t$, is defined, such that $\max\left[h_+^2(\boldsymbol{\theta},t)+h_\times^2(\boldsymbol{\theta},t)\right]$ occurs when $t=0$. 
    The cross polarisation for Eq.~\ref{eq:hplus3} is found by applying a $\pi/2$ phase shift to $\psi_j$.
    More details on this model can be found in Ref.~\cite{Easter2020}.

@@

    We use \textsc{Bilby}, a Bayesian inference package~\cite{Ashton2019}, to obtain posteriors, $p(\boldsymbol{\tilde{\theta}}~|~s_{\varphi,\mathrm{c}}(t))$ from a numerical relativity injection with enforced collapse starting at $t=\tc$ with width $\tw=2$\,ms.
    Posteriors are calculated using waveforms detailed in Eqs.~\ref{eq:hplus3}\Hyphdash*\ref{eq:tukeyfallingedge3}. 
    See Ref.~\cite{Easter2020} for further details of the gravitational-wave likelihood, and Appendix~\ref{appendix:a3} for additional information on the priors.
    \par
    \pagebreak
    To deem the collapse time as successfully recovered, we demand the following to hold: 
\begin{align}
    \tcl - 2\,\mathrm{ms} \leqslant \tc & \leqslant  \tcu + 2\,\mathrm{ms},\\
    \tcu - \tcl & \leqslant  5\,\mathrm{ms},
\end{align}
    where $\tc$ is the injected value. 
    Here $\tcu$ and $\tcl$ are the upper and lower 68 percentile credible intervals on the posterior,  $p(\tc)$.
    Finally, the Bayes Factor for the ratio of evidence for signal against evidence for noise must be $\gg 1$.
    The minimum successful Bayes Factor in favour of a signal over noise in this paper is $\sim\!500$.
    These requirements ensure that successfully recovered $\tc$ are within a few milliseconds of the  injected values. 
    Although this method is somewhat arbitrary, it successfully identifies injections where the collapse time is recovered.
    Furthermore, as the results are pessimistic, with detections not expected until Cosmic Explorer and Einstein Telescope are online, changing this selection criterior will not substantially change these results. \par

    We perform numerical-relativity injections with the full waveform, Eq.~\ref{eq:scol3}, at a grid of distances and apply the above rules to determine whether we successfully recover $\tc$.
\begin{figure*}
    \centering
    \includegraphics[scale=0.24]{MaximumDistancePanelLabelledGW170817.pdf}
    \caption{Maximum distances for which the collapse time can be measured for different interferometer networks and equations of state. The vertical axis shows different equations of state and interferometer configurations, and the maximum detection distance is shown on the horizontal axis. The numerical-relativity simulations are injected with equations of state SLy (upward pointing triangle) and LS220 (downward pointing triangle). The interferometer configurations are 2A+ (blue), 2A+ with the proposed Neutron star Extreme Matter Observatory (orange), Einstein Telescope (green), and Einstein Telescope with Cosmic Explorer~(red). The top panel shows collapse times of 5\,ms, the centre panel 10\,ms and the lower panel 15\,ms collapse times. The  luminosity distance for GW170817 (gravitational-wave only) is shown in shaded grey for comparison~\cite{GW170817multi}.} 
    \label{fig:CollapseTimeDistanceGrid}
\end{figure*} 
\vspace{-0.25cm}    
\section{Results}\label{sec:results3}
    We inject post-merger numerical-relativity waveforms modified to collapse at $t=\tc$ and sample posteriors for $\boldsymbol{\tilde{\theta}}$.
    We then calculate posterior waveforms, $h_{\varphi,c}(\boldsymbol{\tilde{\theta}},t)$, from Eqs.~\ref{eq:hcol3}\Hyphdash*\ref{eq:tukeyfallingedge3}.
    Fig.~\ref{fig:TimeResponse} shows example posterior waveforms for the plus polarisation (left panels) and collapse-time posterior distributions (right panels) for numerical-relativity injections using an SLy equation of state with equal-mass $1.35\,\mathrm{M}_\odot$ progenitor neutron stars.
    The three panels have $\tc=5$\,ms (upper panels), $\tc=10$\,ms (centre panels), and $\tc=15$\,ms (lower panels).
    The left panels show the numerical-relativity injection (plus polarisation) in black and the posterior waveforms in blue.
    The vertical black lines show the beginning, $t=\tc$ (solid), and the end, $t=\tc+\tw$ (dashed), of the collapse for the injected signal.
    We perform injections into the 2A+ detector network at a grid of distances  and from these injections we select three distances where we can clearly recover the collapse time (see Sec.~\ref{sec:methodology3}).
    The injection distances are 5.93\,Mpc for 5\,ms, 3.04\,Mpc for 10\,ms, and 1.00\,Mpc for 15\,ms.
    The right panels show posteriors, $p(\tc)$, in shaded blue, along with the true injected value, $\tc$, as solid vertical black lines.
    The model successfully recovers both the collapse time and the complex nature of the numerical-relativity injection, for all three injections.
    For reference, the full posteriors for $\tc=10\,$ms are shown in the appendix (Fig.~\ref{fig:FullCorner}).\par

@@

    For most collapse times and interferometer configurations, the ratio of the detection distance for LS220 to SLy injections is around $\sim\!1.2\approx f_0(\mathrm{SLy}) / f_0(\mathrm{LS220})$ ($f_0$ is the dominant post-merger oscillation frequency) which is consistent with SLy being softer and more compact than the LS220 equation of state. 
    For $\tc\!\sim15$\,ms injections into either 2A+ with NEMO, ET, or ET with CE, interferometer networks, the ratio of the LS220 to SLy detection distance increases to $\sim\!3$.
    Specifically, for $\tc\!\sim15$\,ms injections, detection distances of $\sim\!8,16,23$\,Mpc are found for LS220 equation of state with interferometers 2A+ with NEMO, ET, and, ET with CE, respectively.
    The corresponding detection distances for SLy injections are $\sim\!3,5,7$\,Mpc. 
    \par
    For injections where we can recover the collapse time, the dominant post-merger frequency is well constrained at $f_0 \lesssim 2\%$, $f_0 \lesssim 1\%$, and $f_0 \lesssim 0.2\%$ for injections of $\tc=5$\,ms, $\tc=10$\,ms and $\tc=15$\,ms, respectively. 
    Finally, we find no significant correlations between $\tc$ and other model parameters.
    We also attempt to measure the maximum detection distance where we can recover $\tc=20$\,ms and find that limitations in the third-order exponentially-damped sinusoidal model, Eq.~\ref{eq:hplus3}, prevent recovery of such collapse times.
    For $\tc > 15$\,ms signals, the analytical model cannot successfully track the time-domain phase of the gravitational-wave strain.
    This limitation could be overcome by increasing the complexity of the frequency evolution in Eq.~\ref{eq:hplus3}, possibly introducing a quadratic frequency evolution term~\cite{Bose2018}.
    Additionally, unmodelled searches such as \textsc{BayesWave} could be modified to measure the collapse time of the remnant~\cite{Cornish2015,Littenberg2015,Chatziioannou2017,Torres-Rivas2019}.\par
\vspace{-0.25cm}
\section{Discussion}\label{sec:discussion3}

@@

\section{Priors}
\label{appendix:a3}
    The priors are listed in Eqs.~\ref{eq:firstprior3}\Hyphdash*\ref{eq:w013} with $\mathcal{U}(a,b)$ representing a uniform prior distribution from $a$ to $b$. 
    The mode number $j$ is limited to $\lbrace 0,1,2 \rbrace$. 
    The priors in Eqs.~\ref{eq:freqsorting3}\Hyphdash*\ref{eq:w013} are constraining priors. 
    These restrictions are enforced in addition to the standard priors. 
    The priors in Eqs.~\ref{eq:freqsorting3}\Hyphdash*\ref{eq:modesorting3} sort the maximum spectral amplitude of each mode which improves computational stability and mode identification.
    See Ref.~\cite{Easter2020} for more details on mode sorting.
    We find that correlations between $\tc$ , $\tw$, and $T_0$ (the exponential decay time-constant for mode zero) make it very difficult to recover all three parameters simultaneously, even with analytic injections into zero noise.
    Fixing $\tw=2$\,ms allows recovery of all other parameters in both analytical injections with zero noise, and numerical-relativity injections with Gaussian noise.
    % \vfill\null

>>>>

        The gravitational waves from the post-merger remnant are modelled as a third-order, exponentially-damped sinusoid with a linear frequency-drift term. The plus polarisation of the gravitational-wave strain, $h_{+}(\boldsymbol{\theta},t)$, is given by: 
\begin{align}
        h_{+}(\boldsymbol{\theta},t) & = \sum_{j} h_{j,+}(\boldsymbol{\theta},t),\nonumber\\
        h_{j,+}(\boldsymbol{\theta},t) & = 
        H w_j \exp\left[-\frac{t}{T_j}\right] \cos \left(2\pi f_j t\left[1+\alpha_j t\right]+\psi_j \right),\nonumber\\
        \boldsymbol{\theta} & = \{H,w_j,T_j,f_j,\alpha_j,\psi_j :  j \in [0,2] \},\label{eq:hplus3}
\end{align}
    where $\boldsymbol{\theta}$ are the model parameters and $\sum_{j} w_j=1$. 
    Here, $H$ is an overall amplitude scaling factor, $w_j$ is the relative amplitude of the $j$th mode, $T_j$ is the corresponding exponential damping time constant, and $f_j$ is the corresponding frequency.
    The linear frequency-drift term is $\alpha_j$ and the initial phase  is $\psi_j$.
    The time, $t$, is defined, such that $\max\left[h_+^2(\boldsymbol{\theta},t)+h_\times^2(\boldsymbol{\theta},t)\right]$ occurs when $t=0$. 
    The cross polarisation for Eq.(\ref{eq:hplus3}) is found by applying a $\pi/2$ phase shift to $\psi_j$.
    More details on this model can be found in Ref.~\cite{Easter2020}.

@@

    We use \textsc{Bilby}, a Bayesian inference package~\cite{Ashton2019}, to obtain posteriors, $p(\boldsymbol{\tilde{\theta}}~|~s_{\varphi,\mathrm{c}}(t))$ from a numerical relativity injection with enforced collapse starting at $t=\tc$ with width $\tw=2$\,ms.
    Posteriors are calculated using waveforms detailed in Eqs.(\ref{eq:hplus3}\Hyphdash*\ref{eq:tukeyfallingedge3}). 
    See Ref.~\cite{Easter2020} for further details of the gravitational-wave likelihood, and Appendix~\ref{appendix:a3} for additional information on the priors.
    \par
    \pagebreak
    To deem the collapse time as successfully recovered, we demand the following to hold: 
\begin{align}
    \tcl - 2\,\mathrm{ms} \leqslant \tc & \leqslant  \tcu + 2\,\mathrm{ms},\\
    \tcu - \tcl & \leqslant  5\,\mathrm{ms},
\end{align}
    where $\tc$ is the injected value. 
    Here $\tcu$ and $\tcl$ are the upper and lower 68 percentile credible intervals on the posterior,  $p(\tc)$.
    Finally, the Bayes Factor for the ratio of evidence for signal against evidence for noise must be $\gg 1$.
    The minimum successful Bayes Factor in favour of a signal over noise in this paper is $\sim\!500$.
    These requirements ensure that successfully recovered $\tc$ are within a few milliseconds of the  injected values. 
    Although this method is somewhat arbitrary, it successfully identifies injections where the collapse time is recovered.
    Furthermore, as the results are pessimistic, with detections not expected until Cosmic Explorer and Einstein Telescope are online, changing this selection criterior will not substantially change these results. \par

    We perform numerical-relativity injections with the full waveform, Eq.(\ref{eq:scol3}), at a grid of distances and apply the above rules to determine whether we successfully recover $\tc$.
\begin{figure*}
    \centering
    \includegraphics[scale=0.24]{MaximumDistancePanelLabelledGW170817.pdf}
    \caption{Maximum distances for which the collapse time can be measured for different interferometer networks and equations of state. The vertical axis shows different equations of state and interferometer configurations, and the maximum detection distance is shown on the horizontal axis. The numerical-relativity simulations are injected with equations of state SLy (upward pointing triangle) and LS220 (downward pointing triangle). The interferometer configurations are 2A+ (blue), 2A+ with the proposed Neutron star Extreme Matter Observatory (orange), Einstein Telescope (green), and Einstein Telescope with Cosmic Explorer~(red). The top panel shows collapse times of 5\,ms, the centre panel 10\,ms and the lower panel 15\,ms collapse times. The  luminosity distance for GW170817 (gravitational-wave only) is shown in shaded grey for comparison~\cite{GW170817multi}.} 
    \label{fig:CollapseTimeDistanceGrid}
\end{figure*} 
\vspace{-0.25cm}    
\section{Results}\label{sec:results3}
    We inject post-merger numerical-relativity waveforms modified to collapse at $t=\tc$ and sample posteriors for $\boldsymbol{\tilde{\theta}}$.
    We then calculate posterior waveforms, $h_{\varphi,c}(\boldsymbol{\tilde{\theta}},t)$, from Eqs.(\ref{eq:hcol3}\Hyphdash*\ref{eq:tukeyfallingedge3}).
    Fig.~\ref{fig:TimeResponse} shows example posterior waveforms for the plus polarisation (left panels) and collapse-time posterior distributions (right panels) for numerical-relativity injections using an SLy equation of state with equal-mass $1.35\,\mathrm{M}_\odot$ progenitor neutron stars.
    The three panels have $\tc=5$\,ms (upper panels), $\tc=10$\,ms (centre panels), and $\tc=15$\,ms (lower panels).
    The left panels show the numerical-relativity injection (plus polarisation) in black and the posterior waveforms in blue.
    The vertical black lines show the beginning, $t=\tc$ (solid), and the end, $t=\tc+\tw$ (dashed), of the collapse for the injected signal.
    We perform injections into the 2A+ detector network at a grid of distances  and from these injections we select three distances where we can clearly recover the collapse time (see Sec.~\ref{sec:methodology3}).
    The injection distances are 5.93\,Mpc for 5\,ms, 3.04\,Mpc for 10\,ms, and 1.00\,Mpc for 15\,ms.
    The right panels show posteriors, $p(\tc)$, in shaded blue, along with the true injected value, $\tc$, as solid vertical black lines.
    The model successfully recovers both the collapse time and the complex nature of the numerical-relativity injection, for all three injections.
    For reference, the full posteriors for $\tc=10\,$ms are shown in the appendix (Fig.~\ref{fig:FullCorner}).\par

@@

    For most collapse times and interferometer configurations, the ratio of the detection distance for LS220 to SLy injections is around $\sim\!1.2\approx f_0(\mathrm{SLy}) / f_0(\mathrm{LS220})$ ($f_0$ is the dominant post-merger oscillation frequency) which is consistent with SLy being softer and more compact than the LS220 equation of state. 
    For $\tc\!\sim15$\,ms injections into either 2A+ with NEMO, ET, or ET with CE, interferometer networks, the ratio of the LS220 to SLy detection distance increases to $\sim\!3$.
    Specifically, for $\tc\!\sim15$\,ms injections, detection distances of $\sim\!8,16,23$\,Mpc are found for LS220 equation of state with interferometers 2A+ with NEMO, ET, and, ET with CE, respectively.
    The corresponding detection distances for SLy injections are $\sim\!3,5,7$\,Mpc. 
    \par
    For injections where we can recover the collapse time, the dominant post-merger frequency is well constrained at $f_0 \lesssim 2\%$, $f_0 \lesssim 1\%$, and $f_0 \lesssim 0.2\%$ for injections of $\tc=5$\,ms, $\tc=10$\,ms and $\tc=15$\,ms, respectively. 
    Finally, we find no significant correlations between $\tc$ and other model parameters.
    We also attempt to measure the maximum detection distance where we can recover $\tc=20$\,ms and find that limitations in the third-order exponentially-damped sinusoidal model, Eq.(\ref{eq:hplus3}), prevent recovery of such collapse times.
    For $\tc > 15$\,ms signals, the analytical model cannot successfully track the time-domain phase of the gravitational-wave strain.
    This limitation could be overcome by increasing the complexity of the frequency evolution in Eq.(\ref{eq:hplus3}), possibly introducing a quadratic frequency evolution term~\cite{Bose2018}.
    Additionally, unmodelled searches such as \textsc{BayesWave} could be modified to measure the collapse time of the remnant~\cite{Cornish2015,Littenberg2015,Chatziioannou2017,Torres-Rivas2019}.\par
\vspace{-0.25cm}
\section{Discussion}\label{sec:discussion3}

@@

\section{Priors}
\label{appendix:a3}
    The priors are listed in Eqs.(\ref{eq:firstprior3}\Hyphdash*\ref{eq:w013}) with $\mathcal{U}(a,b)$ representing a uniform prior distribution from $a$ to $b$. 
    The mode number $j$ is limited to $\lbrace 0,1,2 \rbrace$. 
    The priors in Eqs.~\ref{eq:freqsorting3}\Hyphdash*\ref{eq:w013} are constraining priors. 
    These restrictions are enforced in addition to the standard priors. 
    The priors in Eqs.~\ref{eq:freqsorting3}\Hyphdash*\ref{eq:modesorting3} sort the maximum spectral amplitude of each mode which improves computational stability and mode identification.
    See Ref.~\cite{Easter2020} for more details on mode sorting.
    We find that correlations between $\tc$ , $\tw$, and $T_0$ (the exponential decay time-constant for mode zero) make it very difficult to recover all three parameters simultaneously, even with analytic injections into zero noise.
    Fixing $\tw=2$\,ms allows recovery of all other parameters in both analytical injections with zero noise, and numerical-relativity injections with Gaussian noise.
    % \vfill\null
